Quantifying Spatially Resolved Hydration Thermodynamics Using Grid Inhomogeneous Solvation Theory [Article v\versionnumber]

### 2023-02-10 manuscript/manuscript.tex
Very minor text changes, remove type = Journal Article from some references.

The output is organized by voxel and sorted according to their x, y, and z coordinates, describing the center point of the voxel.
Energy and entropy quantities are reported in two different ways.
The \inlinecode{\_dens} quantities are normalized by the voxel volume and can be used to compute integrals.
The \inlinecode{\_norm} quantities are instead normalized by the number of solvents in the respective voxel averaged over all considered frames, and are useful to visualize local water properties.
To convert from a \inlinecode{\_norm} quantity $X^k_{norm}$ in voxel $k$ to a \inlinecode{\_dens} quantity $X^k_{dens}$, the following equation can be applied:
\begin{equation}
	X^k_{dens} = \frac{X^k_{norm}}{V^k} \cdot \frac{N^k_{solvent}}{N_{frames}}
\end{equation}
with $V^k$, the volume of voxel $k$, $N^k_{solvent}$, the solvent population in voxel $k$, and $N_{frames}$, the number of simulation frames considered in the GIST analysis.

@@

To run PME-GIST, the \inlinecode{pme} flag to \inlinecode{gist} can be used in \software{cpptraj}.
The output will contain two additional columns: \inlinecode{PME\_dens} and \inlinecode{PME\_norm}.
They contain the potential of solute and solvent evaluated at the solvent positions and divided by two.
Furthermore, the \inlinecode{Eww} and \inlinecode{Esw} columns are also computed using PME, and are reported as usual.
For typical use cases, we recommend using \inlinecode{Eww} and \inlinecode{Esw} over the \inlinecode{PME} column.
\todo{vah: The cpptraj manual says that GIST PME energies cannot be decomposed into Esw and Eww -> what's true? Seems to conflict with what is written in this section.}
\subsection{GIST with non-water solvents}
In References~\cite{Kraml2020,Kamenik2020-gist-macrocycles,Waibl2022-gist-solvents}, an extension of GIST towards solvents other than water is described.

>>>>

The output is organized by voxel and sorted according to their x, y, and z coordinates, describing the center point of the voxel.
Energy and entropy quantities are reported in two different ways.
The \inlinecode{\_dens} quantities are normalized by the voxel volume and can be used to compute integrals.
The \inlinecode{\_norm} quantities are instead normalized by the number of solvents in the respective voxel averaged over all considered frames, and are useful to visualize local water properties.
To convert from a \inlinecode{\_norm} quantity $X^k_{norm}$ in voxel $k$ to a \inlinecode{\_dens} quantity $X^k_{dens}$, the following equation can be applied:
\begin{equation}
	X^k_{dens} = \frac{X^k_{norm}}{V^k} \cdot \frac{N^k_{solvent}}{N_{frames}}
\end{equation}
with $V^k$, the volume of voxel $k$, $N^k_{solvent}$, the number of solvent molecules in $k$ over all simulation frames, and $N_{frames}$, the number of frames.

@@

To run PME-GIST, the \inlinecode{pme} flag to \inlinecode{gist} can be used in \software{cpptraj}.
The output will contain two additional columns: \inlinecode{PME\_dens} and \inlinecode{PME\_norm}.
They contain the potential of solute and solvent evaluated at the solvent positions and divided by two.
Furthermore, the \inlinecode{Eww} and \inlinecode{Esw} columns are also computed using PME, and are reported as usual.
For typical use cases, we recommend using \inlinecode{Eww} and \inlinecode{Esw} over the \inlinecode{PME} column.
\subsection{GIST with non-water solvents}
In References~\cite{Kraml2020,Kamenik2020-gist-macrocycles,Waibl2022-gist-solvents}, an extension of GIST towards solvents other than water is described.
